---
title: "Simulate data"
output: html_notebook
---

```{r}
library(tidyverse)
library(simstudy)

set.seed(2021)
```

In this script, I will take the descriptives from Koopman et al. 2019 

(https://www-sciencedirect-com.eur.idm.oclc.org/science/article/pii/S0920996418306911)

to generate a fake dataset, on top of which the analysis script for the current project
will be preconstructed.

In the final analysis, this section will consist of loading the data and selecting the relevant variables.

### Generate each of the variables used in the analysis

```{r}
n <- 1000

# Simulate responses for three YSR items
sim_ysr <-
  tibble(id = rep(as.character(1:n), each = 3),
         col_names = rep(paste0("ysr_", 1:3), n),
         response  = sample(c(0, 1, 2),
                            size = n*3, replace = T, prob = c(.8, .14, .06))) %>% 
  pivot_wider(names_from = col_names, values_from = response)

# Simulate responses for PQ-16 items
sim_pq <-
  tibble(id = rep(as.character(1:n), each = 16),
         col_names = rep(paste0("pq_", 1:16), n),
         response  = rbinom(n*16, size = 1, prob = .15)) %>% 
  pivot_wider(names_from = col_names, values_from = response)

# Simulate responses for CTQ items
sim_ctq <-
  tibble(id = rep(as.character(1:n), each = 25),
         col_names = rep(paste0("ctq_", 1:25), n),
         response  = sample(c(0, 1, 2, 3, 4), size = n*25, replace = T,
                            prob = c(0.35, 0.3, 0.15, 0.12, 0.08))) %>% 
  pivot_wider(names_from = col_names, values_from = response)

# Simulate responses for 8 subjective sleep questionnaire items
sim_sleep <-
  tibble(id = rep(as.character(1:n), each = 8),
         col_names = rep(paste0("sleep_", 1:8), n),
         response  = sample(c(1, 2, 3, 4, 5), size = n*8, replace = T,
                            prob = c(0.35, 0.3, 0.15, 0.12, 0.08))) %>% 
  pivot_wider(names_from = col_names, values_from = response)
 
# Simulate the rest of the variables and combine in a full dataframe
sim_df <-
  tibble(
  id = as.character(1:n),
  # Covariates
  age = rnorm(n, mean = 16, sd = 2),
  sex = sample(c("male", "female"), size = n, replace = T, prob = c(.5, .5)),
  ethnicity = sample(c("dutch", "other western", "non-western"),
                     size = n, replace = T, prob = c(.85, .055, .095)),
  recent_ale = rbinom(1000, size = 60, prob = .055),
  mom_educt = sample(c("no education", "high school", "higher education"),
                     size = n, replace = T, prob = c(0.18, .321, .661)),
  mom_depr = truncnorm::rtruncnorm(n, mean = 0.2, sd = 0.4, a = 0),
  # Outcomes
  # subj_sleep = rnorm(n, mean = 11, sd = 2.5),
  duration_sleep = rnorm(n, 8, 0.51),
  efficiency_sleep = rnorm(n, 82.3, 5.2),
  # arousal_sleep = rnorm(n, 24.3, 3.3), 
  social_jetlag = rnorm(n, 0.75, 1.01)) %>% 
  # Item-level predictors (to be summed later)
  left_join(sim_ysr, by = "id") %>% 
  left_join(sim_pq, by = "id") %>% 
  left_join(sim_ctq, by = "id") %>% 
  left_join(sim_sleep, by = "id") %>% 
  # Configure higher education as the ref category in mother's education variable
  mutate(mom_educt = fct_relevel(mom_educt, "higher education"))

```

### Simulate missing data

```{r}
# Which variables should have missing data
vars_miss <- c("ethnicity", "mom_depr", "recent_ale",
               paste0("sleep_", 1:8), paste0("ctq_", 1:25),
               paste0("pq_", 1:16), paste0("ysr_", 1:3))

# simulate some missing data with 5% probability (default of ampute)
sim_miss <-
  sim_df %>% 
  select(vars_miss) %>% 
  mice::ampute(mech = "MCAR")

# Add some completely missing questionnaires/actiwatch data
missing_df <-
  sim_df %>% 
  select(-vars_miss) %>% 
  bind_cols(sim_miss$amp) %>% 
  mutate(actiwatch_miss = rbinom(1000, size = 1, prob = 0.05),
         questionnaire_miss = rbinom(1000, size = 1, prob = 0.05),
         ctq_miss = rbinom(1000, size = 1, prob = 0.05),
         pq_miss = rbinom(1000, size = 1, prob = 0.05),
         across(sleep_1:sleep_8,
                ~ifelse(questionnaire_miss == 1, NA, .)),
         across(ctq_1:ctq_25,
                ~ifelse(ctq_miss == 1, NA, .)),
         across(pq_1:pq_16,
                ~ifelse(pq_miss == 1, NA, .)),
         across(duration_sleep:social_jetlag,
                ~ifelse(actiwatch_miss == 1, NA, .))) %>% 
  select(-ends_with("miss"))

```

### Save simulated data 

```{r}
write_csv(missing_df, "sim_data.csv")
```

